Title

### 2024-03-07 Quarto Template.qmd

```{r setup}
#| include: false
library(tidyverse)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Dropbox/Work/Vigers/CF",
  "Windows" = "C:/Users/timvigers/Dropbox/Work/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning}
```

>>>>

```{r setup}
#| include: false
library(tidyverse)
switch(Sys.info()[["sysname"]],
  Windows = {
    home_dir <- "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF"
  },
  Darwin = {
    home_dir <- "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF"
  }
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning}

```
